cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Added Mobius data

@@

>>>>

The `gen_gaussian(n, p, s)` function generates a multivariate Gaussian cloud in $p$-dimensional space, centered at the origin with user-defined covariance structure.

Each point is independently drawn using the multivariate normal distribution with:

$$
X_i \sim \mathcal{N}_p(\boldsymbol{0}, \Sigma)
$$

where $\Sigma$ is a user-defined $p \times p$ positive-definite matrix.

@@

The `gen_longlinear(n, p)` function simulates a high-dimensional linear structure with a dominant linear trend and small additive noise.

Each variable $X_i$ is created as:

$$
X_i = \text{scale}_i \cdot \left(0, 1, \dots, n{-}1 + \epsilon\right) + \text{shift}_i
$$

where:

$\text{scale}_i \sim \mathcal{U}(-10, 10)$: randomly chosen direction and stretch.

$\text{shift}_i \sim \mathcal{U}(-300, 300)$: large offset to spread features apart.

$\epsilon \sim \mathcal{N}(0, 0.03 \cdot n)$: Gaussian noise scaled to dataset size to introduce mild irregularity.
